---
title: "analysis"
author: "Joshua Rosenberg"
date: "9/13/2018"
html_document:
    toc: true
    toc_depth: 2
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, messages = FALSE, warning = FALSE)
```

# Update on qualitative coding

## Item #13 - Please explain the one or two technology competencies that you consider as being most important to your individual work as a teacher educator.

## Loading, setting up

In this section, we start out by doing:

```{r, load-packages, message = FALSE}
library(tidyverse)
library(ggridges)
library(corrr)
library(clipr)
library(apaTables)
```

Read the data:

```{r, load-data, eval = TRUE}
# d <- read_csv("tetcs-survey-export.csv", skip = 0)
d <- read_csv("full-tetcs-dataset.csv")
d <- d %>% slice(-c(1:2))
```

Check that the data loaded:

```{r, check-that-data-loaded}
d
```

Process the TETCs variables:

```{r}
# this is only the TETCs
ds <- d %>% 
    dplyr::select(Q11_1:Q11_12) %>% 
    set_names(1:12) %>% 
    mutate_all(str_extract, "\\(?[0-9,.]+\\)?") %>% 
    mutate_all(as.integer) %>% 
    set_names(str_c("v", 1:12))

# this is for the descriptives

ds %>% 
    summarize_all(funs(mean, sd), na.rm = TRUE) %>%
    gather(key, val) %>% 
    separate(key, into = c("var", "stat")) %>% 
    spread(stat, val) %>% 
    mutate(TETC = str_sub(var, start = 2),
           TETC = as.integer(TETC)) %>% 
    arrange(TETC) %>% 
    mutate(TETC = str_c("TETC", TETC)) %>% 
    mutate(mean = round(mean, 3),
           sd = round(sd, 3)) %>% 
    mutate(mean_sd = str_c(mean, " (", sd, ")")) %>% 
    dplyr::select(mean_sd) %>% 
    clipr::write_clip()

# correlations among TETCs
ds %>% 
    set_names(str_c("TETC", 1:12)) %>% 
    corrr::correlate() %>% 
    corrr::shave() %>% 
    corrr::fashion() %>% 
    write_csv("TETC-corrs.csv")

# p-values
ds %>% 
    set_names(str_c("TETC", 1:12)) %>% 
    as.matrix() %>% 
    Hmisc::rcorr() %>% 
    pluck(3)
```

# Demographics

## Years of experience

```{r}
d <-d %>%
    mutate(Q5_1=as.integer(Q5_1),
           Q5_2=as.integer(Q5_2)) %>% 
    bind_cols(ds)

ps <- d %>% 
    dplyr::select(years_teach_exp = Q5_1, 
           yeras_te_exp = Q5_2,
           v1:v12) %>% 
    as.matrix() %>% 
    Hmisc::rcorr() %>% 
    pluck(3) %>% 
    as.data.frame() %>% 
    dplyr::select(1:2) %>% 
    slice(3:nrow(.)) %>% 
    unlist() %>% 
    p.adjust(method = "hochberg") %>% 
    matrix(ncol = 2) %>% 
    as_tibble() %>%
    set_names(c("years_tch_exp", "years_te_experience")) %>% 
    mutate_all(~ ifelse(. < .05, "*", ""))

rs <- d %>% 
    dplyr::select(years_teach_exp = Q5_1, 
           yeras_te_exp = Q5_2,
           v1:v12) %>% 
    as.matrix() %>% 
    Hmisc::rcorr() %>% 
    pluck(1) %>% 
    as.data.frame() %>% 
    dplyr::select(1:2) %>% 
    slice(3:14) %>% 
    set_names(c("years_tch_exp", "years_te_experience"))

data.frame(v1 = str_c(round(rs$years_tch_exp,2), ps$years_tch_exp),
           v2 = str_c(round(rs$years_te_experience,2), ps$years_te_experience)) %>% 
    clipr::write_clip()

cs <- d %>% 
    dplyr::select(years_teach_exp = Q5_1, 
           yeras_te_exp = Q5_2,
           v1:v12) %>% 
    corrr::correlate() %>% 
    corrr::shave() %>% 
    corrr::fashion()

dcc <- d %>% 
    dplyr::select(years_teach_exp = Q5_1, 
           yeras_te_exp = Q5_2,
           v1:v12)
```

```{r}
dss <- ds %>% 
    gather(key, val) %>% 
    mutate(key = str_replace(key, "v", "TETC-"))

dss$key = with(dss, reorder(key, val, mean, na.rm = TRUE))

dss %>% 
    ggplot(aes(x = reorder(key, val), y = val)) +
    geom_violin() +
    # geom_jitter() +
    theme_bw() +
    ylab("Value") +
    xlab(NULL) +
    ylim(1, 5)
```

```{r}
dss <- ds %>% 
    gather(key, val) %>% 
    mutate(key = str_replace(key, "v", "TETC-"))

dss$key = with(dss, reorder(key, val, mean, na.rm = TRUE))

dss %>% 
    ggplot(aes(y = key, x = val)) +
    geom_density_ridges(scale = .9) +
    theme_bw() +
    ylab("Value") +
    xlab(NULL) +
    xlim(1, 5)
```

```{r}
summary(aov(val~key, data = dss))
```

```{r}
# fit1 = hotelling.test(. ~ is_sync, data = ds)
# fit1

#str_c(round(mean(dd$val, na.rm = TRUE), 3), " (", round(sd(dd$val, na.rm = TRUE), 3), ")")
summary(aov(val ~ key, data = dd))

dd <- ds %>% 
    gather(key, val) %>% 
    mutate(key = str_replace(key, "v", "TETC-")) %>% 
    mutate(key = factor(key, levels = c("TETC-4", "TETC-12", "TETC-3", "TETC-2", "TETC-7", "TETC-6", "TETC-1", "TETC-10", "TETC-5", "TETC-9", "TETC-11", "TETC-8")))

d <- ds %>% 
    gather(key, val) %>% 
    mutate(key = str_replace(key, "v", "TETC-")) %>% 
    group_by(key) %>% 
    summarize(mean_val = mean(val, na.rm = TRUE),
              sd_val = sd(val, na.rm = TRUE)) %>% 
    arrange(desc(mean_val))

d %>% 
    ggplot() +
    geom_jitter(data = dd, aes(x = reorder(key, val), y = val), alpha = .5, color = "gray") +
    geom_point(aes(x = reorder(key, mean_val), y = mean_val), size = 2.5) +
    geom_errorbar(aes(x = reorder(key, mean_val),
                      ymin = mean_val-sd_val,
                      ymax = mean_val+sd_val)) +
    theme_bw() +
    ylab("Value") +
    xlab(NULL)

ggsave('tetc-plot.png', width = 8, height = 6)
```

## Grade level

```{r}
# d  %>% 
#     count(Q7) %>% 
#     arrange(desc(n))%>% 
#     write_csv("grade-levels.csv")

m <- read_csv("grade-levels-m.csv")
m <- m %>% set_names(c("Q7", "Q7n", "Q7_code"))

d <- d %>% left_join(m, by = "Q7")

dd <- d %>% dplyr::select(v1:v12, Q7_code)
c <- cbind(dd[, 1:12])
m <- manova(as.matrix(c) ~ dd$Q7_code)
summary(m)

library(broom)

d %>% 
    dplyr::select(v1:v12) %>% 
    map(~ aov(. ~ d$Q7_code)) %>% 
    map_df(tidy) %>% 
    filter(term != "Residuals") %>% 
    mutate(var = str_c("v", 1:12)) %>% 
    dplyr::select(var, sumsq, statistic, p.value) %>% 
    mutate(p.value_adj = p.adjust(p.value, method = "hochberg"))

d %>% 
    dplyr::select(v1:v12) %>% 
    map(~ aov(. ~ d$Q7_code)) %>% 
    map(TukeyHSD) %>% 
    map_df(tidy) %>% 
    mutate(var = rep(1:12, each = 6)) %>% 
    mutate_if(is.numeric, round, 3) %>% 
    mutate(est_p = ifelse(adj.p.value < .001, str_c(estimate, "***"),
                          ifelse(adj.p.value < .01, str_c(estimate, "**"),
                                 ifelse(adj.p.value < .05, str_c(estimate, "*"), estimate)))) %>%     dplyr::select(var, comparison, est_p) %>% 
    spread(comparison, est_p) %>%
    write_csv("grade-tukey.csv")

```

```{r}
dm <- d %>% 
    dplyr::select(Q7_code, v1:v12) %>% 
    gather(key, val, -Q7_code)

x <- aov(val ~ Q7_code*key, data = dm)
apa.aov.table(x)

x
TukeyHSD(x) %>% 
    pluck(1) %>% 
    as.data.frame() %>% 
    rownames_to_column("comparison")

summary(aov(val ~ Q7_code*key, data = dm))

d %>% 
    dplyr::select(Q7_code, v1:v12) %>% 
    gather(key, val, -Q7_code) %>% 
    group_by(Q7_code) %>% 
    summarize(mean = mean(val, na.rm = TRUE),
              sd = sd(val, na.rm = TRUE))

# ggplot(aes(x = reorder(Q7_code, mean), y = mean, ymin = mean - ((1.96*sd)/sqrt(336)), ymax = mean +((1.96*sd)/sqrt(336)))) +
#     geom_col() +
#     geom_errorbar() +
#     theme_bw() +
#     xlab("Grade Level") +
#     ylab("Mean TETC value")
# 
# ggsave("grade-plot-1.png", width = 6, height = 4)
```

## Content area/subject

```{r}
d %>%
    count(Q8) %>% 
    arrange(desc(n)) %>% 
    write_csv("subject.csv")

m <- read_csv("subject-m.csv")
m <- m %>% set_names(c("Q8", "Q8n", "Q8_code")) %>% mutate(Q8_code = ifelse(Q8_code == "STEM", "Science and Math", Q8_code))

d <- d %>% left_join(m, by = "Q8")
```

```{r}
dd <- d %>% dplyr::select(v1:v12, Q8_code)
c <- cbind(dd[, 1:12])
m <- manova(as.matrix(c) ~ dd$Q8_code)
summary(m)

d %>% 
    dplyr::select(v1:v12) %>% 
    map(~ aov(. ~ d$Q8_code)) %>% 
    map_df(tidy) %>% 
    filter(term != "Residuals") %>% 
    mutate(var = str_c("v", 1:12)) %>% 
    dplyr::select(var, sumsq, statistic, p.value) %>% 
    mutate(p.value_adj = p.adjust(p.value, method = "hochberg")) %>% 
    mutate_if(is.numeric, round, 3)

d %>% 
    dplyr::select(v1:v12) %>% 
    map(~ aov(. ~ d$Q8_code)) %>% 
    map(TukeyHSD) %>% 
    map_df(tidy) %>% 
    mutate(var = rep(1:12, each = 6)) %>% 
    mutate_if(is.numeric, round, 3) %>% 
    mutate(est_p = ifelse(adj.p.value < .001, str_c(estimate, "***"),
                          ifelse(adj.p.value < .01, str_c(estimate, "**"),
                                 ifelse(adj.p.value < .05, str_c(estimate, "*"), estimate)))) %>% 
    dplyr::select(var, comparison, est_p) %>% 
    spread(comparison, est_p) %>%
    write_csv("subject-tukey.csv")
```

```{r}
dm <- d %>% 
    dplyr::select(Q8_code, v1:v12) %>% 
    gather(key, val, -Q8_code)

aov(val ~ Q8_code*key, data = dm)
summary(aov(val ~ Q8_code*key, data = dm))
x <- aov(val ~ Q8_code*key, data = dm)

apa.aov.table(x, "subject.doc")

x
TukeyHSD(x) %>% 
    pluck(1) %>% 
    as.data.frame() %>% 
    rownames_to_column("comparison")
TukeyHSD(x)

d %>% 
    dplyr::select(Q8_code, v1:v12) %>% 
    gather(key, val, -Q8_code) %>% 
    group_by(Q8_code) %>% 
    summarize(mean = mean(val, na.rm = TRUE),
              sd = sd(val, na.rm = TRUE))

# ggplot(aes(x = reorder(Q8_code, mean), y = mean)) +
#     geom_col() +
#     geom_errorbar(aes(ymin = mean - ((1.96*sd)/sqrt(336)), ymax = mean +((1.96*sd)/sqrt(336)))) +
#     theme_bw() +
#     xlab("Subject") +
#     ylab("Mean TETC value")
# 
# ggsave("subject-plot.png", width = 6, height = 4)
```

# Joining data - this is to join the qualitative data (not run right now)

```{r, eval = TRUE}
library(googlesheets)
g <- gs_title("Copy of Teacher Education Technology Competencies Survey_November 12, 2018")
```

```{r}
d2 <- gs_read(g, ws = 2, skip = 1)
d2 <- d2 %>% rename(Q13 = `Please explain the one or two technology competencies that you consider as being most important to your individual work as a teacher educator.`) %>% slice(-c(338:339))
d2 <- d2 %>% set_names(c("Q13", str_c("Q13-", names(d2)[-1])))
d2 <- d2 %>% filter(!duplicated(Q13))

d3 <- gs_read(g, ws = 3, skip = 1)
d3 <- d3 %>% rename(Q14 = `Please explain one or more of the technology competencies that you consider of low or no importance to your individual work as a teacher educator.`) %>% slice(-c(338:339))
d3 <- d3 %>% set_names(c("Q14", str_c("Q14-", names(d3)[-1])))
d3 <- d3 %>% filter(!duplicated(Q14))

d4 <- gs_read(g, ws = 4, skip = 1)
d4 <- d4 %>% rename(Q15 = `What is important in your work related to educational technology that is not reflected in the TETCs?`) %>% slice(-c(338:339))
d4 <- d4 %>% set_names(c("Q15", str_c("Q15-", names(d4)[-1])))
d4 <- d4 %>% filter(!duplicated(Q15))
```

```{r}
dx <- d %>% 
    left_join(d2) %>% 
    left_join(d3) %>% 
    left_join(d4)

c13 <- dx %>% 
    dplyr::select(v1:v12, `Q13-1`:`Q13-12`) %>% 
    mutate(TETC = )
    mutate_all(replace_na, 0) %>% 
    corrr::correlate() %>% 
    slice() %>% 
    fashion() %>% 
    dplyr::select(v1:v12) %>% 
    slice(13:24)

c13p <- dx %>% 
    dplyr::select(v1:v12, `Q13-1`:`Q13-12`) %>% 
    mutate_all(replace_na, 0) %>% 
    as.matrix() %>% 
    Hmisc::rcorr() %>% 
    pluck(3) %>% 
    as.data.frame() %>% 
    slice() %>% 
    dplyr::select(v1:v12) %>% 
    slice(13:24)

c14 <- dx %>% 
    dplyr::select(v1:v12, `Q14-1`:`Q14-12`) %>% 
    mutate_if(is.character, as.numeric) %>% 
    mutate_all(replace_na, 0) %>% 
    as.matrix() %>% 
    Hmisc::rcorr() %>% 
    pluck(3) %>% 
    as.data.frame() %>% 
    slice() %>% 
    dplyr::select(v1:v12) %>% 
    slice(13:24)

c14p <- dx %>% 
    dplyr::select(v1:v12, `Q14-1`:`Q14-12`) %>% 
    mutate_all(replace_na, 0) %>% 
    as.matrix() %>% 
    Hmisc::rcorr() %>% 
    pluck(3) %>% 
    as.data.frame() %>% 
    slice() %>% 
    dplyr::select(v1:v12) %>% 
    slice(13:24)

dd <- data.frame(var = str_c("TETC", 1:12),
                 most_imp_r = as.numeric(diag(as.matrix(c13))),
                 most_imp_r_p = as.numeric(diag(as.matrix(c13p))),
                 least_imp_r = as.numeric(diag(as.matrix(c14))),
                 least_imp_r_p = as.numeric(diag(as.matrix(c14p)))
)

write_csv(dd, "most-least-imp-corr.csv")
```

```{r}

```
