---
title: "TETC Analysis Resubmission"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading, setting up

In this section, we start out by doing:

```{r, load-packages, message = FALSE}
library(tidyverse)
library(corrr)
library(broom)
library(patchwork) # devtools::install_github("thomasp85/patchwork")
library(psych)
library(apaTables)
library(nFactors)
library(onewaytests)

usethis::use_git_ignore("*.csv")
```

Read the data:

```{r, load-data, eval = TRUE}
d <- read_csv("full-tetcs-dataset.csv")
d <- d %>% slice(-c(1:2))
# add row name ID
d$id <- 1:nrow(d)
```

Check that the data loaded:

```{r, check-that-data-loaded, eval = FALSE}
d
```

# Merge grade data

```{r}
s <- read_csv("grade-levels-m.csv")

d <- d  %>% 
    left_join(s, by = "Q7") %>% 
    rename(Q7_code = code)
```

# Merge subject data

```{r}
s <- read_csv("subject-m.csv")

d <- d  %>% 
    left_join(s, by = "Q8") %>% 
    rename(Q8_code = code)
```

# Process the TETCs variables

```{r}
d <- d %>% 
    dplyr::rename(v1 = Q11_1,
                  v2 = Q11_2,
                  v3 = Q11_3,
                  v4 = Q11_4,
                  v5 = Q11_5,
                  v6 = Q11_6,
                  v7 = Q11_7,
                  v8 = Q11_8,
                  v9 = Q11_9,
                  v10 = Q11_10,
                  v11 = Q11_11,
                  v12 = Q11_12)

d <- d %>% 
    mutate_at(vars(v1:v12), str_extract, "\\(?[0-9,.]+\\)?") %>% 
    mutate_at(vars(v1:v12), as.integer)

# joining composite
tetc_composite_var <- d %>% 
    dplyr::select(id, v1:v12) %>% 
    gather(key, val, -id) %>% 
    group_by(id) %>% 
    summarize(tetc_composite = mean(val))

d <- d %>% 
    left_join(tetc_composite_var)

# removing one person who didn't respond to TETC items
d <- d %>% 
    filter(!is.na(tetc_composite))
```

# Assumptions

- independence
- normality
- equal variances

```{r}
# For the descriptives

d %>%
    dplyr::select(v1:v12) %>%
    summarize_all(funs(mean, sd), na.rm = TRUE) %>%
    gather(key, val) %>%
    separate(key, into = c("var", "stat")) %>%
    spread(stat, val) %>%
    mutate(TETC = str_sub(var, start = 2),
           TETC = as.integer(TETC)) %>%
    arrange(TETC) %>%
    mutate(TETC = str_c("TETC", TETC)) %>%
    mutate(mean = round(mean, 3),
           sd = round(sd, 3)) %>%
    mutate(mean_sd = str_c(mean, " (", sd, ")")) %>%
    dplyr::select(mean_sd) %>%
    write_csv("tetc-item-descriptives.csv")

```

# Correlations among TETCs

```{r}

d %>% 
    dplyr::select(v1:v12) %>% 
    set_names(str_c("TETC", 1:12)) %>% 
    corrr::correlate() %>% 
    corrr::shave() %>% 
    corrr::fashion() %>% 
    write_csv("TETC-corrs.csv")

# p-values for the correlations
d %>% 
    dplyr::select(v1:v12) %>% 
    as.matrix() %>% 
    Hmisc::rcorr() %>% 
    pluck(3)
```

# Factor analysis

```{r}
ds <- d %>% 
    dplyr::select(v1:v12)

f <- function(d) {
    ev <- eigen(cor(d)) # get eigenvalues
    ap <- parallel(subject=nrow(d),var=ncol(d),
                   rep=100,cent=.05)
    nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
    plotnScree(nS)
}

# this is for the parallel analysis
f(ds[complete.cases(ds), ])

# loadings
o1 <- fa(ds, nfactors = 1)

tibble(Item = str_c("TETC ", 1:12), Loading = as.vector(o1$loadings)) %>%
    mutate(Loading = round(Loading, 2)) %>%
    write_csv("tetc-loadings.csv")

# scree plot
tibble(n = 1:length(o1$e.values),
       eigenvalues = o1$e.values) %>% 
    ggplot(aes(x = n, y = eigenvalues)) +
    geom_point() +
    geom_line() +
    geom_hline(yintercept = 1, linetype = 'dashed') +
    theme_bw() +
    scale_x_discrete(limit = 1:12) +
    xlab("factor")

ggsave("scree.png", width = 6, height = 4)
```

# Descriptives of pre- and in-service teachers

```{r}
d %>% 
    mutate(pre_service = str_detect(Q3, "Pre"),
           in_service = str_detect(Q3, "In")) %>% 
    count(pre_service, in_service) %>% 
    mutate(prop = n/sum(n)) %>% 
    arrange(desc(prop))
```

# Grade

```{r}
d  %>%
    count(Q7) %>%
    arrange(desc(n))%>%
    write_csv("grade-levels.csv")

car::leveneTest(tetc_composite ~ Q7_code, data = d)

grade_aov <- aov(tetc_composite ~ Q7_code, data = d)
summary(grade_aov)
apa.aov.table(grade_aov)

car::leveneTest(tetc_composite ~ Q8_code, data = d)

dd <- d %>% 
    dplyr::select(tetc_composite, Q7_code) %>% 
    mutate(Q7_code = as.factor(Q7_code))

out <- welch.test(tetc_composite ~ Q7_code, data = dd)
paircomp(out)

TukeyHSD(grade_aov) %>% 
    pluck(1) %>% 
    as.data.frame() %>% 
    rownames_to_column("comparison")

TukeyHSD(grade_aov)

# for mean values and sd
grade_desc <- d %>% 
    dplyr::select(Q7_code, v1:v12) %>% 
    gather(key, val, -Q7_code) %>% 
    group_by(Q7_code) %>% 
    summarize(mean = mean(val, na.rm = TRUE),
              sd = sd(val, na.rm = TRUE))

grade_plot <- grade_desc %>% 
    ggplot(aes(x = reorder(Q7_code, mean), y = mean, ymin = mean - ((1.96*sd)/sqrt(336)), ymax = mean +((1.96*sd)/sqrt(336)))) +
    geom_col(fill = "gray") +
    geom_errorbar() +
    theme_bw() +
    xlab("Grade Level") +
    ylab("Mean TETC value") +
    theme(text = element_text(size = 18)) +
    scale_x_discrete(labels = c("Elementary (n = 58)", 
                                "Secondary (n = 76)",
                                "Other (n = 46)",
                                "All (n = 156)")) +
    xlab(NULL) + 
    coord_flip() +
    ggtitle("Grade")

grade_plot 

ggsave("grade-plot-1.png", width = 6, height = 4)
```

## Subject

```{r}
d %>%
    count(Q8_code) %>% 
    arrange(desc(n)) %>% 
    write_csv("subject.csv")

d_for_subject <- d %>% 
    filter(!is.na(Q8_code))

subject_aov <- aov(tetc_composite ~ Q8_code, data = d_for_subject)
summary(subject_aov)
apa.aov.table(subject_aov)

dd <- d %>% 
    dplyr::select(tetc_composite, Q8_code) %>% 
    mutate(Q8_code = as.factor(Q8_code))

out <- welch.test(tetc_composite ~ Q8_code, data = dd)
paircomp(out)

TukeyHSD(subject_aov) %>% 
    pluck(1) %>% 
    as.data.frame() %>% 
    rownames_to_column("comparison")

TukeyHSD(subject_aov)

# same diffs are diff from zero
DTK::DTK.test(x = d_for_subject$tetc_composite, 
              f = d_for_subject$Q8_code)

# for mean values
subject_desc <- d %>% 
    filter(!is.na(Q8_code)) %>% 
    dplyr::select(Q8_code, v1:v12) %>% 
    gather(key, val, -Q8_code) %>% 
    group_by(Q8_code) %>% 
    summarize(mean = mean(val, na.rm = TRUE),
              sd = sd(val, na.rm = TRUE))

subject_plot <- subject_desc %>% 
    ggplot(aes(x = reorder(Q8_code, mean), y = mean, ymin = mean - ((1.96*sd)/sqrt(336)), ymax = mean +((1.96*sd)/sqrt(336)))) +
    geom_col(fill = "gray") +
    geom_errorbar() +
    theme_bw() +
    xlab("Subject") +
    ylab("Mean TETC value") +
    theme(text = element_text(size = 18)) +
    scale_x_discrete(labels = c("Humanities & Spec. Ed. (n = 97)", 
                                "Science & Math (n = 73)",
                                "Other (n = 78)",
                                "Technology (n = 42)")) +
    xlab(NULL) + 
    coord_flip() +
    ggtitle("Subject")

subject_plot

ggsave("subject-plot-1.png", width = 6, height = 4)
```

## Combined plots

```{r}
grade_plot + subject_plot + plot_layout(nrow = 1, ncol = 2, heights = 1, 1.15)
ggsave("combined-plot.png", width = 12, height = 7)
```

# Most/least important corrs

```{r}
#d2 <- gs_read(g, ws = 2, skip = 1)
d2 <- readxl::read_excel("qual-coding.xlsx", sheet = 2, skip = 1)
d2 <- d2 %>% rename(Q13 = `Please explain the one or two technology competencies that you consider as being most important to your individual work as a teacher educator.`) %>% slice(-c(338:339))
d2 <- d2 %>% set_names(c("Q13", str_c("Q13-", names(d2)[-1])))
d2 <- d2 %>% filter(!duplicated(Q13))

d3 <- readxl::read_excel("qual-coding.xlsx", sheet = 3, skip = 1)
d3 <- d3 %>% rename(Q14 = `Please explain one or more of the technology competencies that you consider of low or no importance to your individual work as a teacher educator.`) %>% slice(-c(338:339))
d3 <- d3 %>% set_names(c("Q14", str_c("Q14-", names(d3)[-1])))
d3 <- d3 %>% filter(!duplicated(Q14))
```

```{r}
dx <- d %>% 
    left_join(d2) %>% 
    left_join(d3)

# t <- dx %>% 
#     dplyr::select(v1:v12, `Q13-1.0`:`Q13-12.0`) %>% 
#     mutate_all(replace_na, 0)

c13 <- dx %>% 
    dplyr::select(v1:v12, `Q13-1.0`:`Q13-12.0`) %>% 
    mutate_all(replace_na, 0) %>% 
    corrr::correlate() %>% 
    slice() %>% 
    fashion() %>% 
    dplyr::select(v1:v12) %>% 
    slice(13:24)

c13p <- dx %>% 
    dplyr::select(v1:v12, `Q13-1.0`:`Q13-12.0`) %>% 
    mutate_all(replace_na, 0) %>% 
    as.matrix() %>% 
    Hmisc::rcorr() %>% 
    pluck(3) %>% 
    as.data.frame() %>% 
    slice() %>% 
    dplyr::select(v1:v12) %>% 
    slice(13:24)

c14 <- dx %>% 
    dplyr::select(v1:v12, `Q14-1.0`:`Q14-12.0`) %>% 
    mutate_all(replace_na, 0) %>% 
    corrr::correlate() %>% 
    slice() %>% 
    dplyr::select(v1:v12) %>% 
    slice(13:24)

c14p <- dx %>% 
    dplyr::select(v1:v12, `Q14-1.0`:`Q14-12.0`) %>% 
    mutate_if(is.character, as.numeric) %>% 
    mutate_all(replace_na, 0) %>% 
    as.matrix() %>% 
    Hmisc::rcorr() %>% 
    pluck(3) %>% 
    as.data.frame() %>% 
    slice() %>% 
    dplyr::select(v1:v12) %>% 
    slice(13:24)

dd <- data.frame(var = str_c("TETC", 1:12),
                 most_imp_r = as.numeric(diag(as.matrix(c13))),
                 most_imp_r_p = as.numeric(diag(as.matrix(c13p))),
                 least_imp_r = as.numeric(diag(as.matrix(c14))),
                 least_imp_r_p = as.numeric(diag(as.matrix(c14p)))) %>% 
    mutate_if(is.numeric, round, 3)

dd

write_csv(dd, "most-least-imp-corr.csv")
```